What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-25 android-stacks.tex
best practices more improvements

There is a long-lasting debate about the pros and cons of checked and unchecked exceptions 
~\cite{javatut,stackoverlow,debate},\footnote{152 questions in Stackoverlow
are related to this debate}. Such debates, however, are mainly based on the developers own experience in
using both types - since there is of a lack empirical studies on their the pros and cons.

>>>>

There is a long-lasting debate about the pros and cons of checked and unchecked exceptions 
~\cite{javatut,stackoverlow,debate},\footnote{152 questions in Stackoverlow
are related to this debate}. Such debates, however, are mainly based on the developers own experience in
using both approaches - since there is a lack of empirical studies on their the pros and cons.
